Scikit-learn: machine learning without learning the machinery

### 2014-05-19 article.tex
tinyurl for movie review dataset

temp, \_ = urlretrieve('http://www.cs.cornell.edu/people/pabo/movie-review-data/review\_polarity.tar.gz')
with tarfile.open(temp) as tar:
    tar.extractall(path='movie\_reviews')
data = load\_files(os.path.join('movie\_reviews', 'txt\_sentoken'))

>>>>

temp, \_ = urlretrieve('http://preview.tinyurl.com/review-tgz')
with tarfile.open(temp) as tar:
    tar.extractall(path='movie\_reviews')
data = load\_files(os.path.join('movie\_reviews', 'txt\_sentoken'))
